### 2014-11-10 tex/precise.tex
Fixed the centering
edits to the equality

\begin{figure*}
\begin{tabular}[c]{c}
\scalebox{1.0}{\usebox{\boxPEQ}} \\
% & \usebox{\boxPEX} \\ \\
%(a) & (b) \\
\end{tabular}
\caption{FIXME: I desperately need a caption!}
\label{fig:eqs}
\end{figure*}

@@

The rewrite rules to compare two references in the symbolic summary
heap are shown in~\figref{fig:eqs}. The equals references-true rewrite
rule returns true when two references $r_0$ and $r_1$ are equal. In
GSE this is a simple comparision of two concrete object references. In
the symbolic summary heap, however, we compare sets of constraint
location pairs pointed to by each reference. Let us consider the
equals reference-true rewrite rule. Here, we construct three sets of
constraints. To construct the first set, $\Phi_\alpha$, we check if
there exist constraint location pairs $(\phi_0, l_0) \in L(r_0)$ and
$(\phi_1, l_1) \in L(r_1)$ such that $l_0$ and $l_1$ are the same.
For all such constraints we create conjunctions of the constraints
$\phi_0 \wedge \phi_1$ and add them to set $\Phi_\alpha$. Intutively
these represent the constraints under which $r_0$ and $r_1$ point to
the same location in the heap. The next set of constraints is $\Phi_0$
which contains a constraints under which $r_0$ points to a
corresponding location $l_i$ such that $r_1$ \emph{does not} point to
$l_i$ under any constraint. Inversely, the set of constraints $\Phi_1$
contains the set of constraints under which $r_1$ points to a
corresponding location $l_j$ and $r_0$ \emph{does not} point to $l_j$
under any constraint.

To the global constraint we add the disjunction of the constraints in
$\Phi_\alpha$ to indicate that if any of the constraints are
satisfiable, then references $r_0$ and $r_1$ can be true. Furthermore,
we had to the global heap constraint, $\phi_g^\prime$, the
conjunctions of negations to the constraints in $\Phi_0$ and
$\Phi_1$. This indicates for locations that are not common to the
references, the negations of their constraints are satisfiable. Before
the rewrite rule returns true the satisfiability of the updated global
heap constraint is checked.

Consider the example in~\figref{fig:initHeap}(c), where we would like
to check if $r_1^i$ and $r_2^i$ are equal. The set of constraint locations 
pairs of the two references are:

@@

\noindent{Finally the global constraint is} 
\[
\phi^\prime = \mathit{true} \wedge  (\phi_{1a}\; \implies\; \neg\phi_{2a} )\wedge (\phi_{1b}\; \implies\; \neg\phi_{2c} )  \wedge \phi_{2b}
\]

>>>>

\begin{figure*}
\begin{center}
\begin{tabular}[c]{c}
\scalebox{1.0}{\usebox{\boxPEQ}} \\
% & \usebox{\boxPEX} \\ \\
%(a) & (b) \\
\end{tabular}
\end{center}
\caption{FIXME: I desperately need a caption!}
\label{fig:eqs}
\end{figure*}

@@

The rewrite rules to compare two references in the symbolic summary
heap are shown in~\figref{fig:eqs}. The equals references-true rewrite
rule returns true when two references $r_0$ and $r_1$ \emph{can} be
equal. In GSE semantics checking equality of references is a simple
comparision of two concrete object references. In the symbolic summary
heap, however, we compare sets of constraint location pairs pointed to
by each reference to determine if they could be equal.

Consider the equals reference-true rewrite rule
in~\figref{fig:eqs}. In order to check equality we construct three
sets of constraints. For all constraint location pairs $(\phi_0, l_0)
\in L(r_0)$ and $(\phi_1, l_1) \in L(r_1)$ such that $l_0$ and $l_1$
are the same ($l_0 = l_1$) we create conjunctions of the constraints
$\phi_0 \wedge \phi_1$ and add them to set $\Phi_\alpha$. Intutively,
$\Phi_\alpha$ contains all constraints under which $r_0$ and $r_1$ may
point to the same location in the symbolic summary heap. The second
set, $\Phi_0$, contains constraints under which the reference $r_0$
points corresponding locations such that the reference $r_1$
\emph{does not} point to those locations under any
constraint. Finally, the set, $\Phi_1$, contains constraints under
which $r_1$ points to corresponding locations and $r_0$ \emph{does
  not} point to those locations under any constraint.

We use the three sets of constraints to update the current global heap
constraint $\phi_g$ and create a new global heap constraint
$\phi_g^\prime$. We add to $\phi_g$ the disjunction of the constraints
in $\Phi_\alpha$ to indicate that if any of the constraints are
satisfiable, then references $r_0$ and $r_1$ can be
equal. Furthermore, we had to the global heap constraint,
$\phi_g^\prime$, the conjunctions of negations to the constraints in
$\Phi_0$ and $\Phi_1$. This indicates for locations that are not
common to the references, the negations of their constraints are
satisfiable. Before the rewrite rule returns true we check the
satisfiability of the updated global heap constraint.

Consider the example in~\figref{fig:initHeap}(c). In order to to check
if $r_1^i$ and $r_2^i$ are equal we first get the constraint location
pairs associated with each of the references:

@@

\noindent{Finally the global constraint is} 
\[
\phi^\prime = \mathit{true} \wedge [ (\phi_{1a}\; \wedge\; \phi_{2a} )\vee (\phi_{1b}\; \wedge\; \phi_{2c} ) ] \wedge \neg\phi_{2b} 
\]

\noindent{The equals references-false is the logical dual of the
  reference-true rewrite rule. The references-false is shown
  in~\figref{fig:eqs}.}
